Scaling laws of trophic level and generality vary across latitude

### 2014-06-27 manuscript/latitudepaper.tex
Added a to-do list.

We compiled a list of 345 food webs from the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
\citep{}. Of these, 302 webs had accessible original sources. 
18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
to have different food web properties than webs attempting to
describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
competition-focused networks
\citep{Riede2010}. Of the remaining 230 food webs, we excluded one paleoweb (comprised of probable interactions between 
extinct species) \citep{Simenstad1978} and five ``generalized schemes'' 
\citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
we wished to measure
directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
\citep{Vinogradov1978}, such that it is not clear which site the food web represents. [[[SI table of rejected webs, and why]]] 
[Explain Thompson, Preston, Amundsen separate from Dunne.]
This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans. 
We supplemented these networks with the free-living components of eight high-resolution estuarine food webs \citep{Dunne2013,Thompson2005} and two lake food web \citep{Preston2012,Amundsen2013} that 
included parasites, as well as XX webs that have been used in previous studies of food-web scaling.

>>>>

We compiled a list of 345 food webs from the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
\citep{}. Of these, 302 webs had accessible original sources. 
18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
to have different food web properties than webs attempting to
describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
competition-focused networks
\citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
\citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
we wished to measure
directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
\citep{Vinogradov1978}, such that it is not clear which site the food web represents. [[[SI table of rejected webs, and why]]] 
[Explain Thompson, Preston, Amundsen separate from Dunne.]
This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans. 
We supplemented these networks with the free-living components of eight high-resolution estuarine food webs \citep{Dunne2013,Thompson2005} and two lake food web \citep{Preston2012,Amundsen2013} that 
included parasites, as well as XX webs that have been used in previous studies of food-web scaling.
